Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-06 analysis/paper/paper.Rmd
Remove import_paper functions
We only looked at three areas of reproducibility in the paper, not four

rrpp <- import_notes_paper()
ir <- import_interrater_scores_paper()

@@

```{r scoring, echo=FALSE, message=FALSE, warning=FALSE}
readODS::read_ods(
    system.file(
      "extdata",
      "Reproducibility_in_plant_pathology_notes.ods",
      package = "Reproducibility.in.Plant.Pathology"
    ),
    na = "NA",
    sheet = "scoring_criteria_paper"
  ) %>% 
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  set_table_properties(layout = "autofit") %>%
  set_caption(
    "Articles were three in four areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of four areas, 'Computational Methods Availability', 'Data Availability', 'Software Availability'.")
```

>>>>

rrpp <- import_notes()
ir <- import_interrater_scores()

@@

```{r scoring, echo=FALSE, message=FALSE, warning=FALSE}
readODS::read_ods(
    system.file(
      "extdata",
      "Reproducibility_in_plant_pathology_notes.ods",
      package = "Reproducibility.in.Plant.Pathology"
    ),
    na = "NA",
    sheet = "scoring_criteria_paper"
  ) %>% 
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  set_table_properties(layout = "autofit") %>%
  set_caption(
    "Articles were three in three areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of four areas, 'Computational Methods Availability', 'Data Availability', 'Software Availability'.")
```
